---
title: "Web Scraping With R"
output: html_notebook
author : "RaudhohFitrah"
---

This notebook was made to practice about basic Web Scraping from twitter. Using most popular hashtag as keyword suggested by Twitter.I am open for discussion :)


Step 1 : Load library needed
```{r}
library(rtweet)
```


Step 2 : Setup customer secret key and access token  (Replace with yours)
```{r}
token <- create_token(
  consumer_key = "xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx",
  consumer_secret = "xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx",
  access_token = "xxxxx-xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx",
  access_secret = "xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx")
```

Step 3 : Define (Developer) Username
```{r}
my_username : 'raudhohfitra_h'

```

Step 4 : Scrapping process using "TAEMINinJKT" which has 22.1 K Tweets by 23/8/19
```{r}
tweet <- search_tweets(q = "#TAEMINinJKT", n = 1000)
```

Step 5 : Inspect scrapping result (I)
```{r}
colnames(tweet)
```


6. Inspect scrapping result 
```{r}
res <- tweet[,c("created_at", "screen_name", "text", "country","place_full_name")]

head(res)

```
7. And Finally export to CSV
```{r}
write.csv(res, "Taemin.csv")
```
